### 2019-12-26 paper/educ_work_over_time.tex
Add initial Sanskritization discussion

Almost all of the urban women working are paid either cash or a combination of
cash and in-kind for their work (see Appendix Figure XX).
Rural women have become more likely to receive cash for their labor over time and
the better educated the more likely they are to receive cash.
Despite this, women across all groups have become substantially more likely to 
work for a family member rather than for themselves or somebody else
(see Appendix Figure XX).
Hence, most of the reduction in the likelihood of working appear have come from 
a retraction from the general labor market and self-employment.

@@

[How would education levels behave relative to each other?
- longer among better educated because of sex selection
- convergence because better educated can space children closer together without 
  substantially increased child mortality risk.
- Sanskritization (?) would mean that lower caste caste women try to mimic 
  and with increasing education that becomes easier]

>>>>

Almost all of the urban women working are paid either cash or a combination of
cash and in-kind for their work (see Appendix Figure XX).
Rural women have become more likely to receive cash for their labor over time and
the better educated the more likely they are to receive cash.

Despite this, women across all groups have become substantially more likely to 
work for a family member rather than for themselves or somebody else
(see Appendix Figure XX).
Hence, most of the reduction in the likelihood of working appear have come from 
a retraction from the general labor market and self-employment.

@@

- Sanskritization (?) would mean that lower caste caste women try to mimic 
  and with increasing education that becomes easier]

A major question is how the dramatic changes in educational attainment for women, the
changes in labor force participation, and declining fertility interact.
Especially, in many countries increasing female education is associated with 
improved status in the household and lower fertility.
However, with the increase in male education and income in India over time, 
``Sanskritization'' imply that as lower castes females gain access to education we 
instead observe the adoption of higher caste norms such as stronger son preference
and a retraction from the formal labor market for women 
\citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
In addition, ``Sanskritization'' may lead to not just an increased preference for sons,
but also an increased aversion to daughters, and, in turn, to lower desired fertility
\citep{Borooah2004}.
